Reply To Examiners

### 2014-05-10 answer_thesis_examiner/chap2.tex
auto

\replyToComment
    {Add references to the following statement: ``most of these data processing techniques are traditionally designed for additive and homoskedastic data.''}
    {TODO:CITE}

>>>>

\replyToComment
    {Add references to the following statement: ``most of these data processing techniques are traditionally designed for additive and homoskedastic data.''}
    {Reference added: most of these data processing techniques are traditionally designed for additive and homoskedastic data \cite{Dutch_LNCS_2004}.}
